Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-06 paper/paper-nature_format.qmd
updated paper version

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where is the Speaker tells that MP to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

Our database contains one comma-separated value (CSV) and one parquet file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022. We developed four scripts to produce these files. Each script parses Hansard documents from a specific portion of the 1998 to 2022 time frame.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

@@

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child-node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by an MP, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the MP who made each statement, such as their party and electorate.

In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node. Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes. This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`chamber.xscript//debate//speech/talk.text`" to extract all speeches, in their entirety, at once. This difference in nesting structure made many components of our second script unusable for processing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.

Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly. The reason we did not use its `<speech>` child-node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days. The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data. For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

![First 10 rows of lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}

@@

[^2]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

![10 rows of pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}

@@

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first,speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package. Details on the usage of `uniqueID` will be provided in @sec-usage. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Finally, the `order` variable was added to maintain the order of proceedings.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each CSV file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages.

Further, the `name.id` variable found in each CSV is another unique identifier for each MP. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.

>>>>

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

Our database contains one comma-separated value (CSV) file and one parquet file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022. We developed four scripts to produce these files. Each script parses Hansard documents from a specific portion of the 1998 to 2022 time frame.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

@@

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations. After the `<talk.text>` element closes, there are typically a series of other child nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by an MP, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the MP who made each statement, such as their party and electorate.

In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node. Rather than this single child node that contains all speech content, statements are categorized in individual child nodes. This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`chamber.xscript//debate//speech/talk.text`" to extract all speeches, in their entirety, at once. This difference in nesting structure made many components of our second script unusable for processing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.

Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly. The reason we did not use its `<speech>` child node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days. The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data. For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:

@@

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech. Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`. We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.

@@

![First 10 rows of the lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}

@@

[^2]: While most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}

@@

Due to the fact that the names of MPs with common surnames were not all in their complete form when we flagged for interjections the first time, it was possible that the name of the MP whose turn it was to speak was transcribed in different forms within their speech. For example,  “Smith, Tony, MP” at the start and then “Mr Smith” later on in the speech. By the nature of how we flagged for interjections, this means that rows where the short form like “Mr Smith” is the name would be flagged as an interjection, which is incorrect. To fix this, we re-flagged interjections using the same definition as before, once all names were filled in with this script.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package. Details on the usage of `uniqueID` will be provided in @sec-usage. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Finally, the `order` variable was added to maintain the order of proceedings.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages.

Further, the `name.id` variable found in each file is another unique identifier for each MP. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.
